---
title: "Homework 5"
author: "mm5951"
date: "`r Sys.Date()`"
output: github_document
---

```{r, include = FALSE, message=FALSE, warning=FALSE}
library(tidyverse)
library(rvest)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Solutions provided by teaching team.


## Problem 2

### Data wrangling & description 

I first describe the raw data using the `str()` and `skimr::skim()` functions.

```{r}
homicide_df_raw = read_csv("./data/homicide-data.csv")

str(homicide_df_raw)
skimr::skim(homicide_df_raw)
```

The "homicide_df_raw" dataset contains `ncol(homicide_df_raw)` variables and `ncol(homicide_df_raw)` observations. Details on the nature of its variables and summary values are found in the outputs above.

Then, I import the dataset using `read_csv()`, drop empty observations ("", "na", "Unknown") and wrangle data as per problem instructions. This includes:

* Create a new "city_state" variable (e.g. “Baltimore, MD”) with `mutate()` and order by alphabetical orden using `str_c()`.
* Create a new "resolution" variable using the `case_when()` syntaxis, indicating whehter a case is resolved or not (those for which the disposition is “Closed without arrest” or “Open/No arrest”).

```{r}
homicide_df = read_csv("./data/homicide-data.csv", na = c("","Unknown")) %>% 
  mutate(city_state = str_c(city, state, sep = ", "),
         resolution = case_when(
           disposition == "Closed without arrest" ~ "unsolved",
           disposition == "Open/No arrest" ~ "unsolved",
           disposition == "Closed by arrest" ~ "solved"
         )) %>% 
  relocate(city_state) %>% 
  filter(city_state != "TulsaAL")
```

**PENDING** : Then summarize within cities to obtain the total number of homicides and the number of unsolved homicides.


### Baltimore city estimates 

Prompt: For the city of Baltimore, MD, use the prop.test function to estimate the proportion of homicides that are unsolved; save the output of prop.test as an R object, apply the broom::tidy to this object and pull the estimated proportion and confidence intervals from the resulting tidy dataframe.

```{r}
baltimore_df = homicide_df %>% 
  filter(city_state == "BaltimoreMD")
baltimore_summary = 
  baltimore_df %>% 
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )
baltimore_test = prop.test(
  x = baltimore_summary %>% pull(unsolved), 
  n = baltimore_summary %>% pull(n))
baltimore_test %>% 
  broom::tidy()
```


### Iteration on multiple cities estimates 

Prompt: Now run prop.test for each of the cities in your dataset, and extract both the proportion of unsolved homicides and the confidence interval for each. Do this within a “tidy” pipeline, making use of purrr::map, purrr::map2, list columns and unnest as necessary to create a tidy dataframe with estimated proportions and CIs for each city.

First, Write a function.

```{r}
prop_test_function = function(city_df) {
  
  city_summary = 
    city_df %>% 
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = prop.test(
    x = city_summary %>% pull(unsolved), 
    n = city_summary %>% pull(n))
  
  return(city_test)
}
```

Second, iterate across all cities.

```{r}
results_df = 
  homicide_df %>% 
  nest(data = uid:resolution) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  select(city_state, tidy_results) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))
```

### Data visualization

Prompt: Create a plot that shows the estimates and CIs for each city – check out geom_errorbar for a way to add error bars based on the upper and lower limits. Organize cities according to the proportion of unsolved homicides.

Make a plot showing estimates and confidence intervals for each cities and organize cities according to the proportion of unsolved homicides.

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  labs(title = "Estimates of Proportions of Homicides 
       that are Unsolved and Confidence Interval for Each Cities") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1),
        plot.title = element_text(hjust = 0.5))
```



## Problem 3

To be completed